### 2020-04-04 07-discussion.tex
widehat

\noindent
Please note, that prefixes of process $P_{a_1}$ end with the channel name $a_2$, as the link chain is now connected with the  reaction of  $rs2$.
The translation for the entities follows.
\[
\begin{array}{lclcl}
\llbracket s \rrbracket &\defeq &P_{s} &\defeq & \startchain{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{\noact}\chainedlink{\noact}{{\color{blue}\hat{s}_i}}\chainend{{\color{blue}\hat{s}_o}}.P_{s} + \startchain{s_i}\chainend{s_o}.\overline{P_{s}}\\
&& \overline{P_{s}}&\defeq &\startchain{\overline{s}_i}\chainedlink{\overline{s}_o}{\noact}\chainedlink{\noact}{\hat{s}_i}\chainend{\hat{s}_o}.P_{s}+\startchain{\overline{s}_i}\chainend{\overline{s}_i}.\overline{P_{s}}\\
%\begin{array}{lclclll}
\llbracket x \rrbracket &\defeq & P_{x}& \defeq &\startchain{\tilde{x}_i}\chainend{\tilde{x}_o}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{\tilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%\\
%\\
&& \overline{P_{x}}&\defeq &\startchain{{\color{gray}\tilde{x}_i}}\chainend{{\color{gray}\tilde{x}_o}}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\end{array}
%\]
%
%\[

@@

\[
\begin{array}{lcl}
\llbracket a_2\rrbracket \defeq P_{a_2}&\defeq &\startchain{a_2}\chainedlink{y_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\noact}}\chainedlink{{\color{red}\noact}}{\tilde{ss}_o}\chainend{\silent}.P_{a_2}+
\startchain{a_2}\chainedlink{\overline{y}_i}{\noact}\chainedlink{\noact}{\overline{y}_o}    
\chainedlink{dss_i}{\noact}\chainedlink{\noact}{dss_o}\chainend{\silent}.P_{a_2}\\
%\end{array}
%\]
%
%\[
%\begin{array}{lcl}
%\llbracket r2_2\rrbracket \defeq P_{r2_2}&\defeq &\startchain{r2_2}\chainedlink{ss1}{\noact}\chainedlink{\noact}{ss1}\chainedlink{\tilde{s3}}{\noact}\chainedlink{\noact}{\tilde{s3}}\chainend{\silent}.P_{r2_2}
%+
%\startchain{r2_2}\chainedlink{\overline{ss1}}{\noact}\chainedlink{\noact}{\overline{ss1}}\chainend{\silent}.P_{r2_2}\\
\end{array}
\]
\noindent
In the translation of the entities in  $rs2$, we introduce the mechanism that allows the entity
$s$ ($ss$ in $rs2$) to be provided in $rs1$. Every time $ss$ is produced in $rs2$,  a virtual link is
created to synchronise with $rs1$   on link $\link{\hat{s}_i}{\hat{s}_o}$:
\[
\begin{array}{lclcl}
\llbracket ss \rrbracket& \defeq& P_{ss}&\defeq &\startchain{\tilde{ss}_i}\chainedlink{\hat{s}_i}{\noact}\chainedlink{\noact}{\hat{s}_o}\chainend{\tilde{ss}_o}.P_{ss}+
\startchain{dss_i}   \chainend{dss_o}.\overline{P_{ss}} \\

%\end{array}
%\]
%\[
%\begin{array}{lcllcl}
&&\overline{P_{ss}}&\defeq &\startchain{{\color{red}\tilde{ss}_i}}\chainedlink{{\color{red}\hat{s}_i}}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{{\color{red}\hat{s}_o}}\chainend{{\color{red}\tilde{ss}_o}}.P_{ss}
+
\startchain{dss_i}\chainend{dss_o}.\overline{P_{ss}}\\
\llbracket y\rrbracket&\defeq & P_{y}&\defeq &\startchain{{\color{gray}y_i}}\chainend{{\color{gray}y_o}}.\overline{P_{y}} \\
&&\overline{P_{y}}&\defeq &
%\startchain{\overline{y}_i}\chainedlink{\overline{y}_o}{\noact}\chainedlink{\noact}{\tilde{y}_i}\chainend{\tilde{y}_o}.P_{y}
%+ 
\startchain{\overline{y}_i}\chainend{\overline{y}_o}.\overline{P_{y}}
\end{array}
\]
%\[
%\begin{array}{lcllcl}

@@

\noindent
We now assume that the initial system is $S \defeq \restrict{names}(P_{a_1}|P_{a_2}|P_s|P_y|\overline{P_x}|\overline{P_{ss}})$, i.e.
only entities $s$ and $y$ are present. Now, the only possible transition has  the following label (that we report without restriction):
\[
\startchain{\silent}\chainedlink{s_i}{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{s_o}\chainedlink{\tilde{x}_i}{{\color{gray}\tilde{x}_i}}\chainedlink{{\color{gray}\tilde{x}_o}}{\tilde{x}_o} \chainedlink{a_2}{a_2}\chainedlink{y_i}{ {\color{gray}y_i}}\chainedlink{{\color{gray}y_o}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\tilde{ss}_i}}
\chainedlink{{\color{red}\hat{s}_i}}{{\color{blue}\hat{s}_i}}
\chainedlink{{\color{blue}\hat{s}_o}}{{\color{red}\hat{s}_o}}
\chainedlink{{\color{red}\tilde{ss}_o}}{\tilde{ss}_o}\chainend{\silent},
\]
where the black links belong to the prefixes of $P_{a_1}$, and $P_{a_2}$, the blue links belong to $P_s$, the gray links belong to $P_y$, and $\overline{P_x}$ and the red links belong to $\overline{P_{ss}}$.
After the execution, the entity $s$ is still present in $rs1$ as it has been provided by $rs2$.\\

>>>>

\noindent
Please note, that prefixes of process $P_{a_1}$ end with the channel name $a_2$, as the link chain is now connected with the  reaction of  $rs2$.
The translation for the entities follows.
\[
\begin{array}{lclcl}
\llbracket s \rrbracket &\defeq &P_{s} &\defeq & \startchain{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{\noact}\chainedlink{\noact}{{\color{blue}\widehat{s}_i}}\chainend{{\color{blue}\widehat{s}_o}}.P_{s} + \startchain{s_i}\chainend{s_o}.\overline{P_{s}}\\
&& \overline{P_{s}}&\defeq &\startchain{\overline{s}_i}\chainedlink{\overline{s}_o}{\noact}\chainedlink{\noact}{\widehat{s}_i}\chainend{\widehat{s}_o}.P_{s}+\startchain{\overline{s}_i}\chainend{\overline{s}_i}.\overline{P_{s}}\\
%\begin{array}{lclclll}
\llbracket x \rrbracket &\defeq & P_{x}& \defeq &\startchain{\tilde{x}_i}\chainend{\tilde{x}_o}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{\tilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%\\
%\\
&& \overline{P_{x}}&\defeq &\startchain{{\color{gray}\tilde{x}_i}}\chainend{{\color{gray}\tilde{x}_o}}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\end{array}
%\]
%
%\[

@@

\[
\begin{array}{lcl}
\llbracket a_2\rrbracket \defeq P_{a_2}&\defeq &\startchain{a_2}\chainedlink{y_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\noact}}\chainedlink{{\color{red}\noact}}{\tilde{ss}_o}\chainend{\silent}.P_{a_2}+
\startchain{a_2}\chainedlink{\overline{y}_i}{\noact}\chainedlink{\noact}{\overline{y}_o}    
\chainedlink{dss_i}{\noact}\chainedlink{\noact}{dss_o}\chainend{\silent}.P_{a_2}\\
%\end{array}
%\]
%
%\[
%\begin{array}{lcl}
%\llbracket r2_2\rrbracket \defeq P_{r2_2}&\defeq &\startchain{r2_2}\chainedlink{ss1}{\noact}\chainedlink{\noact}{ss1}\chainedlink{\tilde{s3}}{\noact}\chainedlink{\noact}{\tilde{s3}}\chainend{\silent}.P_{r2_2}
%+
%\startchain{r2_2}\chainedlink{\overline{ss1}}{\noact}\chainedlink{\noact}{\overline{ss1}}\chainend{\silent}.P_{r2_2}\\
\end{array}
\]
\noindent
In the translation of the entities in  $rs2$, we introduce the mechanism that allows the entity
$s$ ($ss$ in $rs2$) to be provided in $rs1$. Every time $ss$ is produced in $rs2$,  a virtual link is
created to synchronise with $rs1$   on link $\link{\widehat{s}_i}{\widehat{s}_o}$:
\[
\begin{array}{lclcl}
\llbracket ss \rrbracket& \defeq& P_{ss}&\defeq &\startchain{\tilde{ss}_i}\chainedlink{\widehat{s}_i}{\noact}\chainedlink{\noact}{\widehat{s}_o}\chainend{\tilde{ss}_o}.P_{ss}+
\startchain{dss_i}   \chainend{dss_o}.\overline{P_{ss}} \\

%\end{array}
%\]
%\[
%\begin{array}{lcllcl}
&&\overline{P_{ss}}&\defeq &\startchain{{\color{red}\tilde{ss}_i}}\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{{\color{red}\widehat{s}_o}}\chainend{{\color{red}\tilde{ss}_o}}.P_{ss}
+
\startchain{dss_i}\chainend{dss_o}.\overline{P_{ss}}\\
\llbracket y\rrbracket&\defeq & P_{y}&\defeq &\startchain{{\color{gray}y_i}}\chainend{{\color{gray}y_o}}.\overline{P_{y}} \\
&&\overline{P_{y}}&\defeq &
%\startchain{\overline{y}_i}\chainedlink{\overline{y}_o}{\noact}\chainedlink{\noact}{\tilde{y}_i}\chainend{\tilde{y}_o}.P_{y}
%+ 
\startchain{\overline{y}_i}\chainend{\overline{y}_o}.\overline{P_{y}}
\end{array}
\]
%\[
%\begin{array}{lcllcl}

@@

\noindent
We now assume that the initial system is $S \defeq \restrict{names}(P_{a_1}|P_{a_2}|P_s|P_y|\overline{P_x}|\overline{P_{ss}})$, i.e.
only entities $s$ and $y$ are present. Now, the only possible transition has  the following label (that we report without restriction):
\[
\startchain{\silent}\chainedlink{s_i}{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{s_o}\chainedlink{\tilde{x}_i}{{\color{gray}\tilde{x}_i}}\chainedlink{{\color{gray}\tilde{x}_o}}{\tilde{x}_o} \chainedlink{a_2}{a_2}\chainedlink{y_i}{ {\color{gray}y_i}}\chainedlink{{\color{gray}y_o}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\tilde{ss}_i}}
\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\widehat{s}_i}}
\chainedlink{{\color{blue}\widehat{s}_o}}{{\color{red}\widehat{s}_o}}
\chainedlink{{\color{red}\tilde{ss}_o}}{\tilde{ss}_o}\chainend{\silent},
\]
where the black links belong to the prefixes of $P_{a_1}$, and $P_{a_2}$, the blue links belong to $P_s$, the gray links belong to $P_y$, and $\overline{P_x}$ and the red links belong to $\overline{P_{ss}}$.
After the execution, the entity $s$ is still present in $rs1$ as it has been provided by $rs2$.\\
